---
title: "Format Data for Agency Resources"
output: html_notebook
---


```{r message=FALSE}
library(tidyverse)
library(config)
library(googlesheets4)
library(httr)
```


IMPORTANT!!!! Must run gs4_auth() in console to get credentials to work!


# Purpose

The purpose of this notebook to format the data received from the Community Alignment Specialist for use with the COVID Agency finder shiny app. 


## Import Data

Import the data exactly as it was from the google sheet.

IMPORTANT!!!! Must run gs4_auth() in console to get credentials to work. If necessary, log in to Google account and an Authentication code will be provided to copy and pasted into console. 


```{r}
# helper variables

# Google Sheet
demo_google_sheet <- "https://docs.google.com/spreadsheets/d/1wXGAnRVd1vVQAit0ocTp3Ocqm1ipW51sA6lxe2iNqOg/"

# Service Type Tab Name
serviceTypeSheet <- "Service Type Info"

# Service Domain Tab Name
domainSheet <- "Service Domain"

# Service FactorTab Name
factorSheet <- "service Factors"


```





```{r}
demo_ServiceType <- read_sheet(demo_google_sheet, sheet = serviceTypeSheet)

#"https://docs.google.com/spreadsheets/d/1wXGAnRVd1vVQAit0ocTp3Ocqm1ipW51sA6lxe2iNqOg/edit#gid=545033575"
```